---
title: "Assignment 7"
author: "Tanner Mierow"
date: "2022-09-01"
output: html_document
---
# Load libraries
```{r}
library(dismo)
library(geosphere)
library(raster)
library(sp)

setwd("~/MierowBIOL7263/GIS_Lecture")
```
# Build climate stack and plot it 
```{r}
my_clim_stack <- stack(raster('WORLDCLIM_Rasters/wc2.1_10m_bio_12.tif'), raster('WORLDCLIM_Rasters/wc2.1_10m_bio_18.tif'), raster('WORLDCLIM_Rasters/wc2.1_10m_bio_19.tif'))

my_clim_stack <- stack(raster('WORLDCLIM_Rasters/wc2.1_10m_bio_12.tif'), raster('WORLDCLIM_Rasters/wc2.1_10m_bio_18.tif'), raster('WORLDCLIM_Rasters/wc2.1_10m_bio_19.tif'))

names(my_clim_stack) <- c("annual_precipitation", "precip_warmest_qrtr", "precip_coldest_qrtr")
plot(my_clim_stack)
```
# Choose sites
```{r}
my_sites <- as.data.frame(click(n=10))
```
# Look at sites
```{r}
names(my_sites) <- c('longitude', 'latitude')
my_sites
```
# extract dat from sites
```{r}
env <- as.data.frame(extract(my_clim_stack, my_sites))
env
```
# join env and ur sites data
```{r}
my_sites <- cbind(my_sites, env)
my_sites
```
# Make projection file
```{r}
myCrs <- projection(my_clim_stack) # get projection info
```
# make into points file
```{r}
my_sites_shape <- SpatialPointsDataFrame(coords=my_sites, data=my_sites, proj4string=CRS(myCrs))

my_sites_shape
```

#Plot raster with points
```{r}
plot(my_clim_stack[[2]])

points(my_sites_shape, pch=16)
```

# Generate set of random points for comparions to our selected points/locations
```{r}
bg <- as.data.frame(randomPoints(my_clim_stack, n = 10000))

head(bg)
```
# Name points
```{r}
names(bg) <- c("longitude", "latitude")

head(bg)
```
# Plot points
```{r}
plot(my_clim_stack[[2]])

points(bg, pch='.')
```
# Extract data points
```{r}
bgEnv <- as.data.frame(extract(my_clim_stack, bg))

head(bgEnv)
```
#Train model 
```{r}
pres.bg <- c(rep(1, nrow(my_sites)), rep(0, nrow(bg)))

train_data <- data.frame(pres.bg = pres.bg, rbind(my_sites, bg))
```
# the model
```{r}
my_model <- glm(pres.bg ~ annual_precipitation*precip_warmest_qrtr*precip_coldest_qrtr + I(annual_precipitation^2) + I(precip_warmest_qrtr^2) + I(precip_coldest_qrtr^2),
data = train_data, 
family = "binomial", 
weights = c(rep(1,  nrow(my_sites)), rep(nrow(my_sites)/nrow(bg), nrow(bg))))

Summary(model)

my_world <- predict(
my_clim_stack,
my_model,
type = "response"
)
)
```
#plot world
```{r}
plot(my_world)
points(my_sites_shape, pch=16)
```
#save your world
```{r}
writeRaster(my_world, "My_climate_space/my_world", format = "GTiff", overwrite = TRUE, progess = "text")
```
# Threshold preferred regions
```{r}

my_world_threshold <- my_world >= quantile(my_world, 0.75)
plot(my_world_threshold)
```

##convert all values not equal to 1 to NA
```{r}
my_world_threshold <- calc(my_world_threshold, fun=function(x) ifelse(x==0|is.na(x), NA, 1))
```
# add radnom points to my best sites/env
```{r}
my_best_sites <- randomPoints(my_world_threshold, 10000)

my_best_env <- as.data.frame(extract(my_clim_stack, my_best_sites))
```
#plot values
```{r}
smoothScatter(x=bgEnv$annual_precipitation, y=bgEnv$precip_warmest_qrtr, col = "purple")
points(my_best_env$annual_precipitation, my_best_env$precip_warmest_qrtr, col = "red", pch=16, cex=0.2)
points(my_sites$annual_precipitation, my_sites$precip_warmest_qrtr, pch=16)
legend("bottomright", inset=0.01,legend=c("world", "my niche", "my locations"), pch = 16, col = c("purple", "red", "black"), pt.cex = c(1,0.4,1))
```