---
title: "Assignment 5"
author: "Tanner Mierow"
date: "`r Sys.Date()`"
output: html_document
---
# Upload files
```{r}
library(dplyr)
library(readr)
library(tidyr)

part1 <- read_csv("https://raw.githubusercontent.com/mbtoomey/Biol_7263/main/Data/assignment6part1.csv")

part2 <- read_csv("https://raw.githubusercontent.com/mbtoomey/Biol_7263/main/Data/assignment6part2.csv")
```

# 1. Pivot and merge these two data sets into a single tidy tibble. Export this tibble as a .csv file saved to a folder called “Results” folder within your R project.
```{r}
part1NEW <- part1  %>% pivot_longer(cols = "Sample1_Male_Control":"Sample20_Female_Treatment", names_to = c("Sample#", "Sex", "TreatmentType"), names_sep = "_", values_drop_na = TRUE) %>% pivot_wider(names_from = ID, values_from = value)

part2NEW <- part2 %>% pivot_longer(cols = "Sample16.Treatment":"Sample13.Control", names_to = c("Sample#", "TreatmentType"), names_sep = "\\.", values_drop_na = TRUE) %>% pivot_wider(names_from = ID, values_from = value)

Finaldoc <- part1NEW %>% full_join(part2NEW, by = c("Sample#", "TreatmentType"))

Finaldoc
```
# 2. With this tidy tibble, generate a new tibble of the mean +/- standard deviation of the residual mass (mass/body length) by treatment and sex. Export this tibble as a .csv file saved to a folder called “Results” folder within your R project.
```{r}
part2DOC <- Finaldoc %>% mutate(residual_mass = mass/body_length) %>% group_by(Sex, TreatmentType) %>% summarise(mean = mean(residual_mass, na.rm = TRUE), StandardDev = sd(residual_mass, na.rm = TRUE))

part2DOC
```
